Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-11 ms.tex
I added a weighted average in the phase with wavelength study and also did a phase vs Amplitude.

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835 - 4$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_1_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:t1Spec0835TauRest}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_1_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:t1Spec1821TauRest}
	}
	\caption{Searching for trends in the $t_1$ parameter as a function of wavelength. The possible upward trend is marginal for \shb\ when using the 4$\sigma$ scaling of error bars. In these cases, we have restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
	\label{fig:ampSpec0835TauRestrict}
	\vspace{0.1in}
\end{figure*}

>>>>

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835 - 4$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_1_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:t1Spec0835TauRest}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_1_spectrum_0400perc_err_taurestrict.pdf}
	\label{fig:t1Spec1821TauRest}
	}
	\caption{Searching for trends in the $t_1$ parameter as a function of wavelength. The possible upward trend is marginal for \shb\ when using the 4$\sigma$ scaling of error bars. In these cases, we have restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
	\label{fig:t1SpecTauRestrict}
	\vspace{0.1in}
\end{figure*}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835 - 4$\times \sigma$]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t1_vs_A1_0400perc_err_taurestrict.pdf}
	\label{fig:t1vsA1Spec0835}
	}
\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t1_vs_A1_0400perc_err_taurestrict.pdf}
	\label{fig:t1vsA1Spec1821}
	}
	\caption{Searching for trends in the $t_1$ parameter as a function of Amplitude ($A_1$). No clear trend arises in these correlation plots. As with Figure \ref{fig:t1SpecTauRestrict}, we have used 4$\sigma$ scaling of error bars and restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
	\label{fig:t1vsA1SpecTest}
	\vspace{0.1in}
\end{figure*}
